geoaxe
======

```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  fig.path = "inst/img/",
  fig.width = 5,
  fig.height = 4
)

knitr::opts_knit$set(global.device = TRUE)
```

[![Build Status](https://travis-ci.org/ropenscilabs/geoaxe.svg)](https://travis-ci.org/ropenscilabs/geoaxe)

`geoaxe` - split geospatial objects into pieces

## Install

```{r eval=FALSE}
devtools::install_github("ropenscilabs/geoaxe")
```

```{r}
library("geoaxe")
library("sp")
```

## Spatial Polygons and friends input

Works for only `SpatialPolygons` for now, but aim to include related classes soon.

```{r}
library("rgeos")
wkt <- "POLYGON((-180 -20, -140 55, 10 0, -140 -60, -180 -20))"
poly <- rgeos::readWKT(wkt)
polys <- chop(x = poly)
```

Plot original polygon

```{r}
plot(poly, lwd = 6)
```

Add chopped up polygon bits

```{r fig.keep='last'}
plot(polys, add = TRUE)
```

```{r echo=FALSE, include=FALSE}
dev.off()
```

## Well-Known Text input

```{r}
wkt <- "POLYGON((-180 -20, -140 55, 10 0, -140 -60, -180 -20))"
plot(chop(wkt))
```

```{r echo=FALSE, include=FALSE}
dev.off()
```

## Manipulate number of cells

> plots go left to right, then down, and repeat

```{r}
layout(matrix(c(1,2,3,4), 2, 2, byrow = TRUE))
par(mar = c(1, 0, 1, 0))
plot(chop(wkt, n = 10))
plot(chop(wkt, n = 15))
plot(chop(wkt, n = 20))
plot(chop(wkt, n = 50))
```

```{r echo=FALSE, include=FALSE}
dev.off()
```

## Manipulate cell size

> plots go left to right, then down, and repeat

```{r}
layout(matrix(1:8, 4, 2, byrow = TRUE))
par(mar = c(1, 0, 1, 0))
plot(chop(wkt, size = 2))
plot(chop(wkt, size = 4))
plot(chop(wkt, size = 8))
plot(chop(wkt, size = 15))
plot(chop(wkt, size = 25))
plot(chop(wkt, size = 50))
plot(chop(wkt, size = 100))
plot(chop(wkt, size = 200))
```

```{r echo=FALSE, include=FALSE}
dev.off()
```

## Meta

* Please [report any issues or bugs](https://github.com/ropenscilabs/geoaxe/issues).
* License: MIT
